Portal Forecast

### 2018-05-03 index.Rmd
improve figure descriptions
on main page and evaluation page

This is the forecast for next month's sampling of rodents at Portal.

@@

@@

```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)

>>>>

This is the forecast for next month's sampling of rodents at Portal. The black line indicates the historic total rodent abundance. The blue line indicates the forecasted amount over the next 12 months, along with confidence intervals. This forecast is from the Ensemble model.

@@

Point forecasts and 90% confidence intervals for specific species at the site for the next sampling period.

@@

This figures are similar to the primary Total Abundance forecast above, but for the abundance of three common rodent species. 
```{r highabund_ts_forecasts, echo=FALSE, message=FALSE, warning=FALSE}
most_abund_sp = sp_predictions %>% 
  filter(species != 'total') %>% 
  arrange(desc(estimate)) %>% 
  head(3) %>% 
  select(species)
